\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
11/01/2024 & 0.1 & Add: 3.1, 3.2, 3.3, 3.6\\
11/02/2024 & 0.2 & Update Rev0 draft\\
11/03/2024 & 0.3 & Add 4.1 for Rev0\\
... & ... & ...\\
\bottomrule
\end{tabularx}

\newpage

\tableofcontents

\newpage

\section{Symbols, Abbreviations, and Acronyms}

Refer to Section 1.3 of the Software Requirements Specification (SRS) document
for the list of symbols, abbreviations, and acronyms.

In addition, the following abbreviations are used in this document:\\

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  V\&V & Verification and Validation\\
  \bottomrule
\end{tabular}\\

\newpage

\pagenumbering{arabic}

This document will provide a detailed plan for the Verification and Validation
(V\&V) of Plutos. Below is an overview of what will be covered in this document:
\begin{itemize}
	\item \hyperlink{section.2}{2 General Information}: This section will provide a brief overview of
	the software being tested, its objectives, challenge level, and extras.
	\item \hyperlink{section.3}{3 Plan}: This section will outline the V\&V team roles, the delegation
	of roles to team members, and the V\&V plan.
	\item \hyperlink{section.4}{4 System Tests}: This section will detail the system tests for
	functional and nonfunctional requirements, and traceability between test
	cases and requirements.
	\item \hyperlink{section.5}{5 Unit Test Description}: This section will provide an overview of the
	unit testing scope, unit tests for functional and nonfunctional
	requirements, and traceability between unit tests and modules.
\end{itemize}


\newpage

\section{General Information}

This section will outline the summary of the V\&V document, the objectives of
the process, the challenge level and extras of the project, and the relevant
external documentation that will be referenced in this document.

\subsection{Summary}

This V\&V document outlines the testing approach for Plutos to ensure the
application meets the functional and non-functional requirements outlined in the
SRS document. The verification process will confirm the functionality of
components such as receipt scanning, item recognition, and categorization
function as intended, while validation efforts will focus on ensuring usability,
performance, and security standards are met for an optimal user experience.


\subsection{Objectives}

This subsection will provide an overview of the V\&V objectives that are
in-scope and out-of-scope for the Plutos application.

\subsubsection{In-Scope V\&V Objectives}

The following are the V\&V objectives, outlining what is intended to be verified
or validated as part of the V\&V process: 
\begin{itemize}
	\item \textbf{Accurate Data Extraction and Categorization}: Ensure that the
machine learning (ML) model accurately extracts key information from receipts
and correctly categorizes it by expense type. This is critical to providing
users with precise budgeting insights. The accuracy requirements are denoted in
the Software Requirements Specification (SRS).
	\item \textbf{Seamless User Experience}: Prioritize usability by designing
an intuitive and responsive interface that simplifies the process of scanning
and categorizing receipts. The app should be easy to navigate, allowing users to
view spending summaries effortlessly. 
	\item \textbf{Real-Time Budgeting Feedback} Provide timely updates on
spending habits to make users aware of their financial status. This feature will
empower users to make informed spending decisions based on real-time data.
	\item \textbf{Security and Privacy} Securely handle all user data, with
particular attention to sensitive financial information. This objective includes
encrypting stored data and ensuring compliance with relevant data protection
regulations. 
\end{itemize}

\subsubsection{Out-of-Scope V\&V Objectives}

The following are the V\&V objectives that are out-of-scope due to time or
resource constraints:
\begin{itemize}
	\item \textbf{In-Depth Usability Testing with All User Types} While basic
usability will be validated, comprehensive testing with diverse user
demographics and accessibility concerns is out of scope due to resource
limitations. Feedback gathered post-launch may help inform future usability
improvements. 
	\item \textbf{Verification of External Libraries} The application will use
external libraries for image processing and data handling, assuming these
libraries have been rigorously tested by their developers. We will prioritize
testing our AI model and app functionality rather than the underlying libraries
to focus resources on core functionality. 
	\item \textbf{Accuracy for Poor-Quality Receipts and Non-Common Items}:
Currently, the receipt scanner focuses on high-quality receipts containing
commonly purchased items for students. While expanding the application to
support lower-quality receipts and less common items is planned for future
phases, this enhancement is out of scope for now due to the complexity of
training the ML model during our timeline.

\end{itemize}



\subsection{Challenge Level and Extras}

The challenge level for the project is \textbf{general}. The extras that will be included are: 
\begin{itemize}
	\item \textbf{Requirements elicitation}: Surveys and interviews have been conducted
	as part of developing our Software Requriements Specfication (SRS).
	\item \textbf{Usability testing}: As part of our validation plan, we will conduct
	usability testing in which users will interact with the Plutos application and
	evaluate their experience.
\end{itemize}

\subsection{Relevant Documentation}

The following documents are relevant to the V\&V of Plutos:
\begin{itemize}
	\item
	\href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/ProblemStatementAndGoals/ProblemStatement.pdf}{\textbf{Problem
	Statement and Goals document}}: This document outlines the problem statement
	and goals of the Plutos application, which will considered to ensure the
	V\&V process aligns with the project's purpose and objectives.
	\item
	\href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/SRS/SRS.pdf}{\textbf{Software
	Requirements Specification (SRS) document}}: This document outlines the
	functional and non-functional requirements of the Plutos application,
	serving as the basis for all testing activities.
	\item
	\href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/HazardAnalysis/HazardAnalysis.pdf}{\textbf{Hazard
	Analysis document}}: This document outlines potential hazards and risks
	associated with the Plutos application, which will be considered during V\&V
	to ensure effective risk mitigation.
	\item
	\href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/Design/SoftDetailedDes/MIS.pdf}{\textbf{Module
	Interface Specification (MIS) document}}: This document provides a detailed
	design of the Plutos application, which will be used to inform the
	development of unit tests for each module. \textit{Note: This document is
	yet to be completed as of the time of writing this initial V\&V plan.}
	\item
	\href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/Design/SoftArchitecture/MG.pdf}{\textbf{Module
	Guide (MG) document}}: This document provides a detailed description of the
	software architecture and modules of Plutos, which will guide the
	development of unit tests for each module. \textit{Note: This document is
	yet to be completed as of the time of writing this initial V\&V plan.}
\end{itemize}

\newpage

\section{Plan}

This section introduce the team members involved in the V\&V process and
describe the V\&V plan for the following components:
\begin{itemize}
	\item The SRS
	\item The design
	\item The V\&V
	\item The implementation
\end{itemize}
Following this, there will be a subssections detailing the automated testing and
verification tools, as well as the software validation plan.


\newpage
\subsection{Verification and Validation Team}

There will be a total of 7 distinct roles when it comes to our verification and validation team.
These roles will be split amongst team members and members may share the same secondary roles to facilitate a broader range of tests without overwhelming one person.
This division allows each team member to specialize in a certain aspect of our app when it comes to verification and validation. 
Attached below is a list of roles available in our V\&V group along with the descriptions of what each role entails. \\

\noindent \textbf{V\&V Roles}
\begin{itemize}
	\item Test Case Designer
	\begin{itemize}
		\item Develops detailed test cases for functional requirements, focusing on different aspects such as image quality, data parsing accuracy, and categorization correctness.
		\item Works closely with the other developers to understand key components of the app and to ensure that test cases cover all scenarios, including edge cases.
	\end{itemize}
	\item Quality Assurance Engineer
	\begin{itemize}
		\item Ensures overall quality of the app by performing functional, integration, and system tests.
		\item Coordinates end-to-end testing for receipt scanning and expense categorization workflows.
		\item Collaborates with the Test Case Designer to verify that all test cases have been executed and outcomes meet expected results.
	\end{itemize}
	\item Ai Model Validator
	\begin{itemize}
		\item Focuses on testing the AI model specifically, evaluating its accuracy in parsing text and categorizing expenses.
		\item Conducts model performance assessments under various conditions, such as diverse receipt layouts, lighting conditions, and languages if applicable.
		\item Continuously monitors for model drift and helps recalibrate the model if accuracy degrades over time.
	\end{itemize}
	\item Usability Tester
	\begin{itemize}
		\item Evaluates the app's user interface and user experience for intuitiveness and ease of use.
		\item Conducts usability testing sessions with other students or users in the target demographic (e.g., university students).
		\item Provides feedback on the app's functionality and ensures that user feedback is incorporated into iterative improvements.
	\end{itemize}
	\item Data Integrity Specialist
	\begin{itemize}
		\item Ensures the accuracy and security of the data collected, especially sensitive information such as financial data on receipts.
		\item Verifies that the app correctly anonymizes data if required and that categorization matches expected outputs based on provided datasets.
		\item Works closely with the AI Model Validator to confirm data handling complies with privacy regulations and standards.
	\end{itemize}
	\item Automation Engineer
	\begin{itemize}
		\item Develops automated testing scripts to streamline regression testing and ensure the app functions consistently across different updates.
		\item Automates repetitive tests, especially those related to scanning, categorization, and UI testing, to save time during development sprints.
		\item Coordinates with the Test Case Designer to convert key test cases into automated tests for efficient reuse.
	\end{itemize}
	\item Performance Tester
	\begin{itemize}
		\item Measures and optimizes app's performance, focusing on response time, load time, and battery usage (important for a mobile app).
		\item Conducts stress tests to determine the app's behavior under heavy usage (e.g., scanning multiple receipts in a short period).
		\item Collaborates with developers to troubleshoot and resolve performance bottlenecks.
	\end{itemize}
\end{itemize}

\noindent The following section delegates the roles above to each team member. Note that each team member has a secondary role which may be repeated amongst other members. The secondary
role is to provide additional assistance when it comes to verification and validation and also serves to bring additional confidence that the system is working
as it should. \\

\noindent \textbf{Delegation of V\&V Roles} \\

\hrule
\vspace{10pt}

\textbf{Eric Chen}
\begin{itemize}
	\item Role(s)
	\begin{enumerate}
		\item Test Case Designer
		\item Quality Assurance Engineer
	\end{enumerate}
	\item Responsibilities
	\begin{enumerate}
		\item Creates comprehensive test cases for functional requirements.
		\item Executes tests to ensure all functionalities are covered.
	\end{enumerate}
\end{itemize}

\hrule
\vspace{10pt}

\textbf{Angela Wang}
\begin{itemize}
	\item Role(s)
	\begin{enumerate}
		\item AI Model Validator
		\item Data Integrity Specialist
	\end{enumerate}
	\item Responsibilities
	\begin{enumerate}
		\item Tests the AI model's accuracy in parsing receipts.
		\item Ensures data handling complies with security and privacy standards.
	\end{enumerate}
\end{itemize}

\hrule
\vspace{10pt}

\newpage

\hrule
\vspace{10pt}
\textbf{Fondson Lu}
\begin{itemize}
	\item Role(s)
	\begin{enumerate}
		\item Usability Tester
		\item Quality Assurance Engineer
	\end{enumerate}
	\item Responsibilities
	\begin{enumerate}
		\item Conducts usability tests and collects user feedback.
		\item Supports quality assurance by testing overall workflows and integration.
	\end{enumerate}
\end{itemize}

\hrule
\vspace{10pt}

\textbf{Jason Tan}
\begin{itemize}
	\item Role(s)
	\begin{enumerate}
		\item Automation Engineer
		\item Performance Tester
	\end{enumerate}
	\item Responsibilities
	\begin{enumerate}
		\item Develops automated test scripts for repetitive testing.
		\item Measures app performance under different conditions to optimize speed and efficiency.
	\end{enumerate}
\end{itemize}

\hrule
\vspace{10pt}

\textbf{Payton Chan}
\begin{itemize}
	\item Role(s)
	\begin{enumerate}
		\item Quality Assurance Engineer
		\item Performance Tester
	\end{enumerate}
	\item Responsibilities
	\begin{enumerate}
		\item Coordinates end-to-end testing and verifies the app's functionality.
		\item Focuses on maintaining consistent performance across updates.
	\end{enumerate}
\end{itemize}

\hrule
\vspace{10pt}

\subsection{SRS Verification Plan}

\subsubsection{Approaches for SRS Verifiation}

\begin{itemize}
	\item Peer Review Feedback:
	\begin{itemize}
		\item Each team member will review the SRS individually and provide ad hoc feedback. They will focus on identifying ambiguous language, incomplete requirements, and inconsistencies.
		\item Each reviewer will log feedback in a shared document, categorizing issues by priority (e.g., high, medium, low).
	\end{itemize}
	\item Primary Reviewer Session:
	\begin{itemize}
		\item A primary reviewer from the team, ideally someone with experience in requirements verification, will perform a detailed examination. They will document findings, focusing on critical areas such as requirement clarity, feasibility, and completeness.
	\end{itemize}
	\item External Peer Feedback:
	\begin{itemize}
		\item If possible, solicit feedback from classmates or others familiar with requirements engineering. They can offer objective insights and identify issues that may have been overlooked internally.
	\end{itemize}
\end{itemize}

\newpage

\subsubsection{Structured Internal Review Process}

\begin{itemize}
	\item Initial Team Meeting:\
	\begin{itemize}
		\item Hold a structured review meeting where team members present and discuss major sections of the SRS. Key points of focus should include functional requirements, assumptions, and constraints.
		\item Prepare a set of questions to guide the discussion, such as:
		\begin{itemize}
			\item "Are the requirements unambiguous and complete?"
			\item "Is each requirement feasible and realistic?"
			\item "Do the requirements adequately represent the user's needs?"
			\item "Are there any areas that might be challenging to test or verify?"
		\end{itemize}
	\end{itemize}
	\item Task-Based Inspection:
	\begin{itemize}
		\item Team members can take turns as "inspectors," responsible for a task-based evaluation of key areas:
		\begin{itemize}
			\item Ensuring requirements align with project goals.
			\item Verifying each requirement's testability and clarity.
			\item Checking that the document is organized and easy to navigate.
		\end{itemize}
	\end{itemize}
	\item Issue Tracker:
	\begin{itemize}
		\item Use an issue tracker or a collaborative tool to manage findings and resolutions. Each issue should include:
		\begin{itemize}
			\item A summary of the issue.
			\item Priority level (e.g., high, medium, low).
			\item Suggested resolution steps.
			\item A status field for tracking progress until resolved.
		\end{itemize}
	\end{itemize}
\end{itemize}

\newpage

\subsubsection{SRS Quality Checklist for Verification}
\begin{tabular}{|>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{9cm}|>{\raggedright\arraybackslash}p{2cm}|}
	\hline
	\textbf{Checklist Item} & \textbf{Description} & \textbf{Pass/Fail} \\
	\hline
	Requirements Clarity & All requirements are clear, unambiguous, and written in active voice. & \\
	\hline
	Completeness & The SRS includes all functional and non-functional requirements, assumptions, and constraints. & \\
	\hline
	Consistency & Requirements are consistent across the document, with no contradictory statements. & \\
	\hline
	Testability & Each requirement is formulated so that it can be tested through measurable criteria. & \\
	\hline
	Feasibility & All requirements are realistic and achievable within the project's scope and resources. & \\
	\hline
	Traceability & Each requirement is traceable to a higher-level objective or user need. & \\
	\hline
	Maintainability	& The document is well-organized, with clear headings and numbered requirements for easy referencing. & \\
	\hline
	Priority and Dependencies & Requirements are prioritized, and dependencies are explicitly stated where applicable. & \\
	\hline
	User-Centered Language & Requirements reflect user needs and use terminology consistent with user and stakeholder language. & \\
	\hline
	Compliance with Standards & The SRS complies with any applicable standards or best practices in software requirements engineering. & \\
	\hline

\end{tabular}

\newpage

\subsection{Design Verification Plan}

\subsubsection{Specification Verification}

\noindent \begin{tabular}{|>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{4cm}|>{\raggedright\arraybackslash}p{3cm}|p{1cm}|p{2.25cm}|}
	\hline
	\textbf{Checklist Items} & \textbf{Description} & \textbf{Verification Method} & \textbf{Pass /Fail} & \textbf{Comments} \\ 
	\hline
	Requirements Completeness & Ensure all system and user requirements are addressed in the design. & Requirements Traceability Matrix & & \\
	\hline
	System Requirements Compliance & Verify that design conforms to software/system specifications. & Specification Review	& & \\
	\hline
	Compliance with Standards & Ensure compliance with coding standards, industry best practices, and regulatory guidelines. & Code Review, Standards Checklist	& & \\
	\hline
	Security Requirements & Confirm that the security design follows the requirements, especially for data privacy and user information. & Security Audit & & \\
	\hline
\end{tabular}

\newpage

\subsubsection{Functional Verification}

\noindent \begin{tabular}{|>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{4cm}|>{\raggedright\arraybackslash}p{3cm}|p{1cm}|p{2.25cm}|}
	\hline
	\textbf{Checklist Items} & \textbf{Description} & \textbf{Verification Method} & \textbf{Pass /Fail} & \textbf{Comments} \\ 
	\hline
	Receipt Scanning Capability	& Verify that receipt scanning feature works as expected with various image qualities. & Functional Testing	& & \\
	\hline
	Expense Categorization Accuracy	& Confirm that expenses are correctly categorized by the AI model. & Model Accuracy Testing	& & \\
	\hline
	User Interface (UI) Responsiveness & Ensure that UI elements are responsive across devices and screen sizes. & UI Testing & & \\
	\hline
	Error Handling and Recovery	& Verify that the app gracefully handles errors, such as scanning failures or incorrect categorizations. & Error Simulation	& & \\
	\hline
	Integration with External Services & Confirm integration with any third-party services (e.g., cloud storage or payment platforms). & Integration Testing & & \\
	\hline
\end{tabular}

\newpage

\subsubsection{Performance Validation}

\noindent \begin{tabular}{|>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{4cm}|>{\raggedright\arraybackslash}p{3cm}|p{1cm}|p{2.25cm}|}
	\hline
	\textbf{Checklist Items} & \textbf{Description} & \textbf{Verification Method} & \textbf{Pass /Fail} & \textbf{Comments} \\ 
	\hline
	System Performance Under Load & Test app performance with simultaneous receipt scans to assess system stability and responsiveness.	& Load Testing & & \\
	\hline
	AI Model Processing Time & Measure the average processing time for receipt categorization. & Model Timing Analysis & & \\
	\hline
	Battery and Resource Consumption & Verify that app resource usage is within acceptable limits to preserve device performance and battery life. & Resource Monitoring & & \\
	\hline
	Network Efficiency & Ensure the app handles network limitations (e.g., slow or intermittent connections) without data loss.	& Network Simulation & & \\
	\hline
	Latency for Real-Time Features & Measure latency in real-time features, ensuring a smooth user experience. & Latency Testing & & \\
	\hline
\end{tabular}

\newpage

\subsubsection{Document Validation}

\noindent \begin{tabular}{|>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{4cm}|>{\raggedright\arraybackslash}p{3cm}|p{1cm}|p{2.25cm}|}
	\hline
	\textbf{Checklist Items} & \textbf{Description} & \textbf{Verification Method} & \textbf{Pass /Fail} & \textbf{Comments} \\ 
	\hline
	User Documentation Completeness	& Verify that user manuals, installation guides, and support documentation are complete and accurate. & Documentation Review & & \\
	\hline
	Developer Documentation Completeness & Ensure all developer-focused documentation (e.g., API docs, setup instructions) is detailed and up to date. & Documentation Review & & \\ 
	\hline
	Code Documentation & Confirm that all code modules and functions are documented according to guidelines. & Code Review & & \\
	\hline
	Test Plans and Results & Verify the completeness of test plans and that test results meet required standards. & Test Report Review & & \\
	\hline
	Change Log and Version History & Ensure that the change log and version history are comprehensive and well-documented. & Change Log Review & & \\ 
	\hline
\end{tabular}

\subsection{Verification and Validation Plan Verification Plan}

Creating a Verification and Validation (V\&V) plan for a smart AI budgeting app requires a structured and systematic approach to confirm that the application operates accurately, efficiently, and reliably under real-world conditions.
This app uses advanced AI to parse receipt images, extract relevant information, and categorize expenses, which presents additional challenges for the V\&V process.
Unlike traditional software applications, an AI-driven app requires validation not only of standard software functionalities but also of the AI model's performance in accurately interpreting various receipt formats, layouts, and data entries.
This means that the V\&V plan must address both classic software testing elements (such as unit and integration testing) and specific AI model evaluation techniques, like model validation and performance testing, to ensure that the app delivers consistent results. \\

Given the diverse functionality—spanning expense tracking, budgeting, and financial forecasting—this V\&V approach must encompass both software-level testing and user-centric assessments to verify usability and accuracy from an end-user perspective.
Below is a comprehensive list of recommended V\&V techniques and a corresponding checklist, each tailored to ensure that the budgeting app meets its design specifications and delivers high-quality, reliable outcomes for users.

\subsubsection{V\&V Techniques for Plutos App}
\noindent \begin{enumerate}
	\item \textbf{Requirements Review}: Regular reviews of the Software Requirements Specification (SRS) are essential to confirm that all listed requirements align with the project goals. Stakeholders should validate that these requirements meet user needs.
	\item \textbf{Code Review}: Structured code reviews help to maintain code quality and identify potential issues in the receipt parsing and expense categorization components.
	\item \textbf{Unit Testing}:Unit tests should cover the core functions, especially those related to parsing and categorizing. Test cases should address a range of inputs, including expected, edge, and invalid cases.
	\item \textbf{Integration Testing}: Integration testing ensures that the AI model and app components work together seamlessly, verifying the accuracy and consistency of data processing.
	\item \textbf{System Testing}: System testing is necessary to evaluate the full app functionality, making sure that expense tracking, budgeting, and forecasting features meet the specified requirements.
	\item \textbf{Acceptance Testing}: End-user testing allows the team to validate that the app performs well in real-world settings, especially in accurately parsing receipts of various formats.
	\item \textbf{Mutation Testing}: Mutation testing can be used to check the effectiveness of the test cases and to identify any weaknesses in the testing approach.
	\item \textbf{Regression Testing}: Regression testing is essential to ensure that updates or changes in the AI model or app features do not interfere with existing functionality.
	\item \textbf{User Interface (UI) Testing}: UI testing helps confirm that the app interface is user-friendly, responsive, and consistent across different devices.
	\item \textbf{Model Validation}: The AI model should be validated on labeled data to check its performance, especially for accuracy in categorizing expenses based on parsed information.
	\item \textbf{Performance Testing}: Performance tests can be conducted to measure the app's speed and reliability, especially when processing large receipts or handling multiple users.
	\item \textbf{Security Testing}: Security testing ensures that financial data is stored and transmitted securely, with protections in place for data encryption and user access.
\end{enumerate}

\newpage

\subsubsection{V\&V Plan Checklist (Peer Reviews)}

\begin{itemize}
	\item [\texttt{[ ]}] Review and validate all requirements with stakeholders.
	\item [\texttt{[ ]}] Conduct code reviews and log issues or recommendations.
	\item [\texttt{[ ]}] Develop and execute unit tests covering key parsing and categorization functions.
	\item [\texttt{[ ]}] Perform integration testing for model interactions with the app's front and back end.
	\item [\texttt{[ ]}] Complete system testing across all app functionalities (tracking, budgeting, forecasting).
	\item [\texttt{[ ]}] Facilitate acceptance testing sessions with end users to gather real-world feedback.
	\item [\texttt{[ ]}] Implement mutation testing to strengthen the test suite.
	\item [\texttt{[ ]}] Schedule regular regression testing, especially after updates or model retraining.
	\item [\texttt{[ ]}] Conduct comprehensive UI testing for design consistency across devices.
	\item [\texttt{[ ]}] Evaluate AI model performance, retraining if accuracy is below target.
	\item [\texttt{[ ]}] Measure and optimize performance for speed and reliability under heavy usage.
	\item [\texttt{[ ]}] Perform security testing to protect user financial data.
	\item [\texttt{[ ]}] Document and address all V\&V findings and updates to maintain a high-quality app.
\end{itemize}

\newpage

\subsection{Implementation Verification Plan}

\subsubsection{Verification Techniques}

\begin{enumerate}
	\item \textbf{Code Walkthroughs}:
	\begin{itemize}
		\item \textbf{Purpose}:Collaborative sessions where developers explain their code to peers.
		\item \textbf{Focus Area(s)}: Core functions like receipt parsing, expense categorization, and AI integration.
		\item \textbf{Goal}: Increase team familiarity with code components and detect early logical or design errors.
	\end{itemize}
	\item \textbf{Code Inspections}:
	\begin{itemize}
		\item \textbf{Purpose}: Formal, structured code reviews based on a project-specific checklist.
		\item \textbf{Checklist Criteria}:
		\begin{itemize}
			\item Adherence to coding standards and proper error handling.
			\item Efficient use of resources (especially for image processing and AI tasks).
			\item Consistent structure, naming conventions, and formatting.
		\end{itemize}
		\item \textbf{Goal}: Enforce best practices, maintain code readability, and ensure alignment with functional requirements.
	\end{itemize}
	\item \textbf{Static Analysis}:
	\begin{itemize}
		\item \textbf{Tools}: ESLint, Prettier
		\item \textbf{Checks Performed}:
		\begin{itemize}
			\item Syntax errors, unused code, and code smells.
			\item Security vulnerabilities, especially in data handling and storage.
			\item Code complexity, duplication, and performance.
			\item Maintains a uniform code style so that codebase becomes more readable, navigable and manageable.
		\end{itemize}
		\item \textbf{Goal}: Identify issues automatically, maintain security, and ensure high code quality.
	\end{itemize}
	\item \textbf{Unit Testing}:
	\begin{itemize}
		\item \textbf{Purpose}: Verify that individual functions and components operate correctly in isolation.
		\item \textbf{Key Functions to Test}: Data extraction from receipts, categorization logic, and budget calculations.
		\item \textbf{Coverage Goal}: Achieve >80\% coverage on core functions.
		\item \textbf{Goal}: Ensure reliability and accuracy at the component level.
	\end{itemize}
	\item \textbf{Integration Testing}:
	\begin{itemize}
		\item \textbf{Purpose}: Test interactions between modules to ensure data flows as expected.
		\item \textbf{Key Interactions to Verify}: Data flow between the AI model, backend, and frontend UI.
		\item \textbf{Goal}: Ensure seamless integration of AI functionality with other app components.
	\end{itemize}
	\item \textbf{Regression Testing}:
	\begin{itemize}
		\item \textbf{Purpose}: Prevent new updates from disrupting existing features.
		\item \textbf{Scope}: Entire application with emphasis on areas impacted by recent changes or updates.
		\item \textbf{Process}: Continuously updated regression suite covering core features and AI updates.
		\item \textbf{Goal}: Maintain stability and functionality across iterative changes.
	\end{itemize}
\end{enumerate}


\newpage

\subsection{Automated Testing and Verification Tools}

\begin{enumerate}
	\item \textbf{Unit Testing Frameworks}
	\begin{itemize}
		\item \textbf{Jest}: Jest is the default testing framework for React Native applications. It supports TypeScript, has a rich API for writing unit tests, and comes with built-in mocking capabilities.
		\item \textbf{React Testing Library}: This library works well with Jest for testing React components, focusing on user interactions and component behavior rather than implementation details.
	\end{itemize}
	\item \textbf{Static Analysis Tools}
	\begin{itemize}
		\item \textbf{ESLint}: ESLint is a powerful linter for JavaScript and TypeScript. It can be configured with TypeScript support to enforce coding standards, detect potential errors, and maintain code quality. It can also be extended with plugins for React and serves as industry best practices for JavaScript/TypeScript related-projects.
		\item \textbf{Prettier}: Integrating Prettier alongside ESLint helps ensure consistent code formatting across the codebase, which helps in improving readability.
	\end{itemize}
	\item \textbf{Continuous Integration (CI) Tools}
	\begin{itemize}
		\item \textbf{GitHub Actions}: This tool can be set up to run workflows that execute tests, linters, and builds automatically on every pull request or commit, ensuring that code quality is maintained consistently (i.e. Husky).
		\item \textbf{Jenkins}: Jenkins is an open-source automation server that facilitates continuous integration and continuous deployment processes. It can be configured to automatically run tests, linting, and builds every time code is pushed to the repository, ensuring that code quality is maintained consistently.
	\end{itemize}
	\newpage
	\item \textbf{Test Coverage Tools}
	\begin{itemize}
		\item \textbf{Istanbul (nyc)}: Istanbul is a code coverage tool that integrates with Jest, providing detailed reports on which parts of the codebase are covered by tests, helping to identify untested code.
		\item \textbf{Codecov or Coveralls}: These services can be used to visualize and summarize code coverage metrics after each build, providing insights into overall coverage and trends over time.
	\end{itemize}
	\item \textbf{Profiling Tools}
	\begin{itemize}
		\item \textbf{React Native Performance Monitor:}: This built-in tool in React Native helps track performance metrics such as frame rates and memory usage, providing insights into the app's performance.
		\item \textbf{Flipper}: A platform for debugging mobile apps, Flipper offers a variety of plugins that assist in profiling and monitoring app performance.
	\end{itemize}
	\item \textbf{Mutation Testing}
	\begin{itemize}
		\item \textbf{Stryker}: Stryker is a mutation testing framework for JavaScript and TypeScript. It can help assess the effectiveness of tests by introducing small changes in the code (mutations) and checking if the tests can catch them.
	\end{itemize}
	\item \textbf{Plans for Summarizing Code Coverage Metrics}
	\begin{itemize}
		\item \textbf{Daily/Weekly Reports:}: The CI pipeline can be configured to generate code coverage reports with every build and aggregate these reports weekly. Tools like Codecov can be used to visualize trends over time.
		\item \textbf{Review Meetings}: Regular review meetings can be conducted to discuss coverage metrics with the team, identifying areas needing improvement and setting goals for coverage percentages.
		\item \textbf{Integrate Coverage Reports in PRs}: Coverage reports should be included in pull request reviews, ensuring that any code changes are evaluated in the context of their impact on overall coverage.
	\end{itemize}
\end{enumerate}

\noindent For additional information, please consult the \href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{development plan}.
\subsection{Software Validation Plan}

\begin{enumerate}
	\item \textbf{Objective}
	\begin{itemize}
		\item The objective of this software validation plan is to ensure that the Plutos budgeting app meets all specified requirements and user needs for accurately parsing receipts, categorizing expenses, and generating reliable financial insights. The plan aims to validate the app’s AI-driven capabilities, functional accuracy, security, and overall user experience.
	\end{itemize}
	\item \textbf{Scope} \\
	This validation plan will cover the following main functionalities:
	\begin{itemize}
		\item \textbf{Receipt Parsing and Data Extraction}: Ensuring accurate interpretation of various receipt formats.
		\item \textbf{Expense Categorization}: Validating that extracted data is correctly categorized.
		\item \textbf{Expense Tracking and Budgeting}: Verifying that users can effectively track and budget expenses.
		\item \textbf{Forecasting Capabilities}: Ensuring the app provides meaningful insights for future spending.
		\item \textbf{User Interface (UI) and User Experience (UX)}: Confirming ease of use, responsiveness, and accessibility across devices.
		\item \textbf{Data Security and Privacy}: Verifying secure data handling, storage, and compliance with privacy standards.
	\end{itemize}
	\newpage
	\item \textbf{Validation Techniques}
	The validation process will employ the following techniques to confirm that the software performs as intended and fulfills user requirements.
	\begin{enumerate}
		\item \textbf{Requirements Validation}
		\begin{itemize}
			\item \textbf{Purpose}: Ensure that the system requirements, as outlined in the Software Requirements Specification (SRS), reflect user needs.
			\item \textbf{Techniques}: Requirements review, stakeholder validation sessions.
			\item \textbf{Criteria}: All requirements are verified as achievable, necessary, and aligned with end-user expectations.
		\end{itemize}
		\item \textbf{Functional Testing}
		\begin{itemize}
			\item \textbf{Purpose}: Validate that the app functions correctly and meets the intended use cases.
			\item \textbf{Techniques}:
			\begin{itemize}
				\item \textbf{Unit Testing}: Test each component in isolation (e.g., receipt image processing, data extraction modules).
				\item \textbf{Integration Testing}: Ensure smooth interaction between AI models and application components.
				\item \textbf{System Testing}: Test the app end-to-end, covering all functional requirements.
			\end{itemize}
			\item \textbf{Criteria}: All functional test cases pass, with particular attention to accuracy in parsing receipts and categorizing expenses.
		\end{itemize}
		\item \textbf{Model Validation and AI Performance Testing}
		\begin{itemize}
			\item \textbf{Purpose}: Confirm that the AI model for receipt parsing and categorization meets performance expectations.
			\item \textbf{Techniques}:
			\begin{itemize}
				\item \textbf{Model Evaluation on Labeled Data}: Test the model's accuracy on a labeled dataset of diverse receipts.
				\item \textbf{Performance Benchmarking}: Measure model accuracy, precision, recall, and latency.
				\item \textbf{Error Analysis}: Review misclassifications and parsing errors to refine the model.
			\end{itemize}
			\item \textbf{Criteria}: Model meets or exceeds the required performance metrics (e.g., 90\%+ accuracy in parsing and categorization).
		\end{itemize}
		\item \textbf{Usability Testing}
		\begin{itemize}
			\item \textbf{Purpose}: Validate that users can easily interact with the app and achieve their goals without confusion or frustration.
			\item \textbf{Techniques}:
			\begin{itemize}
				\item \textbf{User Surveys and Feedback Sessions}: Gather direct user feedback on the app's ease of use and intuitiveness.
				\item \textbf{Task-Based Testing}: Have users complete key tasks (e.g., uploading a receipt, viewing categorized expenses).
			\end{itemize}
			\item \textbf{Criteria}: Positive user feedback, with 80\%+ of participants finding the app intuitive and easy to use.
		\end{itemize}
		\item \textbf{Security and Privacy Testing}
		\begin{itemize}
			\item \textbf{Purpose}: Ensure that user data, especially financial information, is stored and handled securely.
			\item \textbf{Techniques}: 
			\begin{itemize}
				\item \textbf{Data Encryption Verification}: Confirm that data is encrypted both in transit and at rest.
				\item \textbf{Access Control Testing}: Validate that only authorized users can access their data.
				\item \textbf{Compliance Testing}: Ensure adherence to relevant privacy regulations (e.g., GDPR).
			\end{itemize}
			\item \textbf{Criteria}: All data protection and compliance measures are met; no security vulnerabilities found.
		\end{itemize}
		\item \textbf{Performance and Load Testing}
		\begin{itemize}
			\item \textbf{Purpose}: Verify the app's responsiveness and stability under expected usage.
			\item \textbf{Techniques}: 
			\begin{itemize}
				\item \textbf{Load Testing}: Simulate high user load to evaluate system performance.
				\item \textbf{Stress Testing}: Test the app's behavior under extreme conditions.
			\end{itemize}
			\item \textbf{Criteria}: App remains functional and responsive under high load, with minimal performance degradation.
		\end{itemize}
		\item \textbf{Regression Testing}
		\begin{itemize}
			\item \textbf{Purpose}: Ensure that new updates or fixes do not break existing functionality.
			\item \textbf{Techniques}: Automated regression test suite that re-tests core functionality after each update.
			\item \textbf{Criteria}:All regression test cases pass, maintaining stability with no loss of functionality.
		\end{itemize}
	\end{enumerate}

	\item \textbf{Validation Schedule} \\

	\noindent \begin{tabular}{|>{\raggedright\arraybackslash}p{3cm}|p{2cm}|>{\raggedright\arraybackslash}p{7cm}|}
		\hline
		\textbf{Phase} & \textbf{Duration} & \textbf{Activities} \\
		\hline
		\textbf{Requirements Review} & 1 week & Validate SRS, confirm requirements with stakeholders \\
		\hline
		\textbf{Functional Testing} & 2 weeks & Develop and execute unit, integration, and system test cases \\
		\hline
		\textbf{Model Validation} & 1 week & Evaluate AI model on diverse receipts, measure performance metrics \\
		\hline
		\textbf{Usability Testing} & 1 week & Conduct usability tests with end-users, gather feedback \\
		\hline
		\textbf{Security Testing} & 1 week & Perform security assessments, validate data encryption and compliance \\
		\hline
		\textbf{Performance Testing} & 3 days & Conduct load and stress tests to evaluate system performance under expected load \\
		\hline
		\textbf{Regression Testing} & Ongoing & Run regression tests after updates to ensure consistent functionality \\
		\hline
	\end{tabular}
	\newpage
	\item \textbf{Deliverables}
	\begin{itemize}
		\item \textbf{Test Case Documentation}: Detailed test cases for all functionalities, covering expected outcomes and pass/fail criteria.
		\item \textbf{Test Execution Report}: Summary of test results, including success rates and any failed test cases.
		\item \textbf{Defect and Issue Log}: Record of identified defects and issues, with resolution status.
		\item \textbf{Usability Feedback Summary}: Report on feedback from usability testing sessions.
		\item \textbf{Validation Summary Report}: Comprehensive report summarizing the validation outcomes, certifying the app's readiness for release.
	\end{itemize}
	\item \textbf{Success Criteria} \\
	The app will be considered validated if it meets the following success criteria:
	\begin{itemize}
		\item All functional test cases passes requirements.
		\item AI model achieves required accuracy in parsing and categorization.
		\item Usability tests show positive user feedback with minimal issues.
		\item No high-severity defects in security, performance, or compliance.
		\item Regression tests show that new updates do not disrupt existing functionality.
	\end{itemize}
\end{enumerate}

\noindent For additional information regarding validation, please consult the \href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/SRS/SRS.pdf}{Software Requirements Specification (SRS)} verification section.

\newpage
\section{System Tests}

\subsection{Tests for Functional Requirements}

The following test cases are divided into subsets corresponding to major functional areas in the application, as detailed in the Software Requirements Specification (SRS) document. 
Each subset addresses a specific functional component, including user account management, receipt scanning and processing, database management, item recognition and categorization, and financial tracking. 
These tests will help verify the functional requirements outlined in the SRS and will help with the creation of those tests to verify the specified functional requirements.

\subsubsection{User Account Management Tests}

This subsection covers tests required to verify tests revolving around user account management. The user account manager allows users to create an account, update it, and log in and out.\\
\textit{Functional Requirements: FR1 - FR5}

\begin{enumerate}

\item{test-UAM-1\\}

\textbf{Description:} The user should be able to create an account with specified name, email address and password

\textbf{Control:} Functional
					
\textbf{Initial State:} The app is on the account creation screen and there is no existing account with the test email
					
\textbf{Input:} Name, valid email, and password
					
\textbf{Output:} Account creation is successful, and the user is redirected to the login screen

\textbf{Test Case Derivation:} This test ensures that the application allows users to create an account. The manager expects a valid name with no numbers or special characters, a valid email (existing email of correct email format) and a password that only contains certain characters to prevent SQL injection
					
\textbf{How test will be performed:} The test will be performed by providing instructions to a user/tester to enter valid name, email and password submissions. They will then determine if the test is successful by verifying that the actual output matches the expected output (as provided in the instructions/referenced in this document)

\item{test-UAM-2\\}

\textbf{Description:} The user should be able to login with valid credentials

\textbf{Control:} Functional
					
\textbf{Initial State:} The app is on the login page and a registered account has been created with the corresponding testing credentials
					
\textbf{Input:} Email and password
					
\textbf{Output:} The app is on the login page and a registered account has been created with the corresponding testing credentials

\textbf{Test Case Derivation:} This test ensures that only authenticated users may access the app's functionalities

\textbf{How test will be performed:} The test will be performed by having a user/tester provide valid credentials to the system and verify that the app redirects them to the home page after successful login

\item{test-UAM-3\\}

\textbf{Description:} The user should be able to logout of the app

\textbf{Control:} Functional
					
\textbf{Initial State:} The user is already logged into the app
					
\textbf{Input:} Logout submission
					
\textbf{Output:} Account logout is successful, and the user is redirected to the login page

\textbf{Test Case Derivation:} This test verifies that the app terminates the user's session and redirects the user to the login page to protect user's account data

\textbf{How test will be performed:} While logged in, a user/tester will click the logout button and observe that the user is redirected to the login screen. Verify that no user-specific data is accessible after logging out

\item{test-UAM-4}

\textbf{Description:} Users should be able to update account information after initial setup

\textbf{Control:} Functional

\textbf{Initial State:} User is logged in and on the account settings screen

\textbf{Input:} Modify fields (e.g., name or password) and save changes

\textbf{Output:} Updated account information is saved and reflected on the profile screen.

\textbf{Test Case Derivation:} The test ensures that users are able to manage and update their account information after initial setup

\textbf{How test will be performed:} A tester/user will modify the account fields, save, and verify that updates are displayed correctly on the profile.

\item{test-UAM-5}

\textbf{Description:} Users should not be able to access the application without
logging in.

\textbf{Control:} Functional

\textbf{Initial State:} The application is open and the user has not logged in.

\textbf{Input:} Attempt to access the application without logging in.

\textbf{Output:} The application should prompt the user to log in.

\textbf{Test Case Derivation:} The test verifies that the application requires
users to log in before accessing its features.

\textbf{How test will be performed:} The tester will attempt to access the
application without logging in and verify that the application prompts them to log
in.

\item{test-UAM-6}

\textbf{Description:} Users should be able to reset their password.

\textbf{Control:} Functional

\textbf{Initial State:} The application is open and the user has not logged in.

\textbf{Input:} Use the application's password reset feature.

\textbf{Output:} The user receives an email with instructions to reset their password.

\textbf{Test Case Derivation:} The test verifies that users can reset their
password.

\textbf{How test will be performed:} The tester will use the application's
password reset feature and verify that they receive an email with instructions
to reset their password.

\end{enumerate}

\subsubsection{Image Processing Tests}

This subsection covers tests required to verify tests revolving around receipt scanning and processing. The receipt scanner allows users to upload and preview images\\
\textit{Functional Requirements: FR8 - FR11}

\begin{enumerate}
\item{test-IP-1\\}

\textbf{Description:} User should be able to upload an image for processing

\textbf{Control:} Functional

\textbf{Initial State:} The application is on the receipt upload screen.

\textbf{Input:} Select and upload a receipt image from the device's file storage

\textbf{Output:} The uploaded image is successfully displayed for preview

\textbf{Test Case Derivation:} The test verifies that users are able to upload images from their device and preview them before receipt scanning

\textbf{How test will be performed:} The user/tester will select an image from storage, upload it, and confirm the image preview correctly displayed

\item{test-IP-2\\}

\textbf{Description:} Users should be able to preview an uploaded image before processing and confirm/reupload the image based on preference

\textbf{Control:} Functional

\textbf{Initial State:} Image is uploaded and displayed as a preview.

\textbf{Input:} Confirm or reupload the previewed image

\textbf{Output:} Confirmed image proceeds to processing, or retake restarts the upload process

\textbf{Test Case Derivation:} Ensures users can review and confirm the uploaded image, as required for accuracy before processing.

\textbf{How test will be performed:} The user/tester previews the image, confirms, and observes if it advances to processing. Alternatively, users can retake and verify they are taken back to the image upload process

\item{test-IP-3\\}

\textbf{Description:} There is a limit to the file size of the image that can be
uploaded.

\textbf{Control:} Functional

\textbf{Initial State:} The application is open and the user is on the image
upload screen.

\textbf{Input:} Attempt to upload an image that exceeds the file size limit.

\textbf{Output:} The application should display an error message indicating that
the file size limit has been exceeded.

\textbf{How test will be performed:} The tester will attempt to upload an image
that exceeds the file size limit and verify that the application displays an
error message.



\end{enumerate}

\subsubsection{Manual Expense Input Tests}

This subsection covers tests that verify functionality for allowing users to manually input their expenses in the case that their receipt is unable to be processed. 
The manual input system is responsible for outlining fields that the user must fill out for their expense(s) to be tracked.\\
\textit{Functional Requirements: FR12-13}

\begin{enumerate}
\item{test-MIS-1\\}

\textbf{Description:} Users should be able to manually input expenses

\textbf{Control:} Functional

\textbf{Initial State:} Image captured or uploaded cannot be processed or the user wants to manually input items from their receipt from the expense tracker view

\textbf{Input:} Entered items, item costs, item quantities, categories and receipt date

\textbf{Output:} Items, quantities, costs, categories and receipt date are correctly processed and displayed 

\textbf{Test Case Derivation:} Ensures users can manually input their receipt/expense in case their image isn't able to be processed or they want to manually input them. The test verifies that manually inputted expense data is processed correctly

\textbf{How test will be performed:} From the expense tracker page, the user/tester will select the "manually input expenses" option and fill out the corresponding fields for category, item, item cost and date. They will then validate that all manual entries have been processed in the finalized expenses screen and match their inputs.	

\end{enumerate}

\subsubsection{Database Management Tests}

This subsection covers tests required to verify functionality for database management. The database managers securely stores user account information and user receipt information.\\
\textit{Functional Requirements: FR14 - FR15}

\begin{enumerate}
\item{test-DM-1\\}

\textbf{Description:} Account information should be protected and securely stored in the database

\textbf{Control:} Automatic

\textbf{Initial State:} Application database is empty or has only encrypted data.

\textbf{Input:} Create a new user account.

\textbf{Output:} User data is stored securely in the database, encrypted.

\textbf{Test Case Derivation:} The test validates that user account information is protected and verifies that the application securely handles user data

\textbf{How test will be performed:} Check database entries post-account creation to verify data encryption and account information

\item{test-DM-2\\}

\textbf{Description:} Receipt data must be securely stored in database

\textbf{Control:} Automatic

\textbf{Initial State:} Application database has no receipt data for the test user.

\textbf{Input:} Upload a receipt image.

\textbf{Output:} Receipt image and extracted data are securely stored in the database.

\textbf{Test Case Derivation:} The test verifies receipt data is securely stored, ensuring data privacy

\textbf{How test will be performed:} Check database entries post-upload to confirm storage security and receipt information
\end{enumerate}

\subsubsection{Item Recognition and Categorization}

This subsection covers tests required to verify functionality for item recognition and categorization from receipt scanning. The receipt scanner is responsible for recognizing and categorizing items from users' uploaded receipts.\\
\textit{Functional Requirements: FR16 - FR18}

\begin{enumerate}
\item{test-RS-1\\}

\textbf{Description:} Uploaded receipts should be processed and all items, their quantities and prices should all be correctly recognized with an accuracy of 90\%

\textbf{Control:} Functional

\textbf{Initial State:} User confirms uploaded receipt is ready to be processed

\textbf{Input:} Run item recognition on a sample receipt

\textbf{Output:} Recognized items, quantities, and prices are displayed accurately

\textbf{Test Case Derivation:} The test verifies the accuracy of the OCR model by identifying items on the inputted receipt

\textbf{How test will be performed:} Process the receipt image and verify recognized details against the original receipt

\item{test-RS-2\\}

\textbf{Description:} Uploaded receipts should categorize items on them under common expense categories (i.e. groceries, entertainment, etc..)

\textbf{Control:} Functional

\textbf{Initial State:} Receipt has been scanned and items are recognized from the receipt

\textbf{Input:} Apply categorization based on item names.

\textbf{Output:} Items are correctly categorized (i.e. milk under "Groceries").

\textbf{Test Case Derivation:} The test validates organized expense tracking accuracy by categorizing items under common expense categories

\textbf{How test will be performed:} Run categorization on a processed receipt and check that items are correctly sorted


\item{test-RS-3\\}

\textbf{Description:} Verify that users can modify receipt data.

\textbf{Control:} Functional

\textbf{Initial State:} Receipt has been scanned and items are recognized and
categorized from the receipt

\textbf{Input:} Modify item names, quantities, prices, and categories.

\textbf{Output:} Manual changes are saved and reflected in the expense tracker.

\textbf{Test Case Derivation:} The test verifies that users can manually modify
receipt data.

\textbf{How test will be performed:} The tester will modify item names,
quantities, prices, and categories and verify that the changes are saved and
reflected in the expense tracker.


\end{enumerate}

\subsubsection{Financial Tracking Tests}

This subsection verifies the functionality of financial tracking features such has spending history and budget management. The financial tracker is responsible for storing users expenses/spendings, as well as allowing users to set and track budgets.\\
\textit{Functional Requirements: FR19 - FR21}

\begin{enumerate}

\item{test-FT-1\\}

\textbf{Description:} Users should be able view spending their spending history by category and trends

\textbf{Control:} Functional

\textbf{Initial State:} Application has recorded user's past expenses and user is on the expense tracking view

\textbf{Input:} Generate spending history overview

\textbf{Output:} Accurate summary of total spending by category and time period

\textbf{Test Case Derivation:} The test verifies users can monitor their budgets through viewing their spending trends

\textbf{How test will be performed:} The tester/user should be able to trigger spending history generation and verify summaries match expected data upon entering the expense tracker view

\item{test-FT-2\\}

\textbf{Description:} Users should be able to set and track their budgets

\textbf{Control:} Functional

\textbf{Initial State:} User is on the budgeting window and no current budget is set for the specified category

\textbf{Input:} Budget limit for a specific category

\textbf{Output:} Budget limit is saved and displayed in tracking

\textbf{Test Case Derivation:} This test confirms the ability for users to set and track budgets

\textbf{How test will be performed:} The tester/user sets a budget for a specific category, then verify it appears and updates as expected in tracking

\item{test-FT-3\\}

\textbf{Description:} Verify that users get notified when they are close to
exceeding their budget or when a goal has been reached.

\textbf{Control:} Functional

\textbf{Initial State:} User has set a budget for a specific category and is
close to exceeding it. OR User is also close to reaching a budgeting goal.

\textbf{Input:} User inputs an expense that would exceed the budget. OR User
inputs an income that would reach a savings goal.

\textbf{Output:} User receives a notification.

\textbf{Test Case Derivation:} The test verifies that users are notified when
they are close to exceeding their budget or when a goal has been reached.

\textbf{How test will be performed:} The tester will input an expense that would
exceed the budget and verify that they receive a notification. The tester will
also input an income that would reach a savings goal and verify that they receive
a notification.

\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

\subsubsection{Accuracy Tests}

This subsection covers tests required to verify the accuracy of the system in processing various financial data.\\
\textit{Nonfunctional Requirements: NFR1 - NFR6}

\begin{enumerate}

\item{test-ACC-1\\}

\textbf{Description:} Verify the accuracy of the machine learning model in
correctly identifying and extracting key information (i.e., item names,
quantities, prices, dates) from receipts.

\textbf{Type:} Manual
					
\textbf{Initial State:} Machine learning model is ready for testing with a
dataset of receipts prepared for evaluation.
					
\textbf{Input/Condition:} Test receipts containing various sets of key
information (item names, quantities, prices, and dates).
					
\textbf{Output/Result:} Model's accuracy measured by the percentage of key
information extracted correctly.
					
\textbf{How test will be performed:} The output will be compared with the
initially inputted test receipts to compare information. The accuracy will be
computed by determining the percentage of correctly identified and extracted
information and will be determined if it meets the 80\% threshold.

\item{test-ACC-2\\}

\textbf{Description:} Verify the accuracy of the machine learning model in
categorizing expenses into predefined categories.

\textbf{Type:} Manual
					
\textbf{Initial State:} Machine learning model is set to have predetermined
expense categories.
					
\textbf{Input/Condition:} A set of receipt transactions with known categories.
					
\textbf{Output/Result:} The model will output the categories of the given
transactions, and the precision will be calculated from this.
					
\textbf{How test will be performed:} The model will process the set of
transactions and compare the assigned categories to the correct ones. Precision
will be measured to see if the 90\% threshold is met.

\item{test-ACC-3\\}

\textbf{Description:} Verify that all monetary calculations maintain a
precision of up to two decimal places.

\textbf{Type:} Automatic
					
\textbf{Initial State:} The application is ready for financial calculations.
					
\textbf{Input/Condition:} A set of monetary calculations (budget changes, new
purchases).
					
\textbf{Output/Result:} The output should display values rounded to two decimal
places.
					
\textbf{How the Test Will Be Performed:} The system will perform different
calculations and verify that all results maintain precision up to two decimal
places as specified.

\item{test-ACC-4\\}

\textbf{Description:} Verify the accuracy of the OCR model in recognizing text
from images of receipts.

\textbf{Type:} Manual
					
\textbf{Initial State:} The OCR model is set to process images of receipts.
					
\textbf{Input/Condition:} A set of receipt images with known text.
					
\textbf{Output/Result:} The OCR model's accuracy in recognizing text is
calculated.
					
\textbf{How the Test Will Be Performed:} The OCR model will process the receipt
images and compare the recognized text to the actual text, ensuring an accuracy
rate of at least 90\%.

\item{test-ACC-5\\}

\textbf{Description:} Verify the accuracy of the application in summing up
expenses, incomes, and savings across different periods and categories.

\textbf{Type:} Manual
					
\textbf{Initial State:} The application is set to calculate expenses, incomes,
and savings.
					
\textbf{Input/Condition:} A dataset of transactions across different periods and
categories.
					
\textbf{Output/Result:} The application's summation accuracy is assessed.
					
\textbf{How the Test Will Be Performed:} The system will input the transaction
data and verify that the calculated totals are accurate, ensuring the
application meets the 99\% accuracy requirement in summation.

\item{test-ACC-6\\}

\textbf{Description:} Verify that data synced across multiple devices is
consistent.

\textbf{Type:} Manual
					
\textbf{Initial State:} The application is up to date. User is logged in.
					
\textbf{Input/Condition:} Financial data entered on one device.
					
\textbf{Output/Result:} Financial data appears on all devices.
					
\textbf{How the Test Will Be Performed:} The tester will input financial data on
one device, sync, and verify that all other devices show the same data to ensure
100\% consistency.

\end{enumerate}

\subsubsection{Performance Tests}

This subsection covers tests required to assess the performance of the application under various conditions.\\
\textit{Nonfunctional Requirements: NFR7 - NFR9}

\begin{enumerate}

\item{test-PERF-1\\}

\textbf{Description:} The application must load user data within five seconds.

\textbf{Type:} Manual
					
\textbf{Initial State:} The system is installed and ready to run.
					
\textbf{Input/Condition:} The application is opened and user data is loaded.
					
\textbf{Output/Result:} User data should load within five seconds.
					
\textbf{How the Test Will Be Performed:} The user/tester will measure the time
taken to load user account data.

\item{test-PERF-2\\}

\textbf{Description:} The application must respond to user actions (e.g., adding
an entry, generating a report) within two seconds.

\textbf{Type:} Manual
					
\textbf{Initial State:} User information has been loaded.
					
\textbf{Input/Condition:} The user will be asked to perform various actions of
their choice on the application.
					
\textbf{Output/Result:} All actions should respond within two seconds.
					
\textbf{How the Test Will Be Performed:} The user/tester will measure the
response time for various user actions.


\item{test-PERF-3\\}

\textbf{Description:} The system must be able to handle a minimum of 10
concurrent users without significant performance degradation.

\textbf{Type:} Manual
					
\textbf{Initial State:} The application is installed and running.
					
\textbf{Input/Condition:} Ten users log into the application simultaneously and
perform typical tasks.
					
\textbf{Output/Result:} The application should maintain performance levels
without significant degradation.
					
\textbf{How the Test Will Be Performed:} The tester will simulate 10 concurrent
users accessing the application and monitor performance metrics (e.g., load
times, response times) to ensure the application performs adequately under load.

\end{enumerate}

\subsubsection{Usability Tests}

This subsection covers tests required to evaluate the usability and user
experience of the application. After each of these tests, the user will be asked
to fill out a usability survey, which can be found in \hyperref[appx.a]{Appendix
A}.\\

\textit{Nonfunctional Requirements: NFR10 - NFR17}

\begin{enumerate}

\item{test-USAB-1\\}

\textbf{Description:} The application must have a clean, intuitive, and
easy-to-navigate interface, allowing users to perform common tasks (e.g., adding
expenses, viewing budgets) within two to three clicks, and complete tasks such
as adding a new receipt or setting a budget limit within 10 seconds on average.

\textbf{Type:} Manual, Usability Testing
					
\textbf{Initial State:} The application is installed, running, and ready for user interaction.
					
\textbf{Input/Condition:} A user with no prior experience attempts to complete key tasks (e.g., uploading a receipt, viewing expense summaries, setting a budget), 
including scenarios where:
  \begin{itemize}
      \item A page fails to load due to network issues
      \item A required field is left blank in a form
      \item A button is disabled without clear explanation
  \end{itemize}
					
\textbf{Output/Result:} Tasks should show completion and result corresponding
outputs.
					
\textbf{How the Test Will Be Performed:} The user/tester will evaluate the
interface by performing tasks and counting the average number of clicks and the
duration taken.

\item{test-USAB-2\\}

\textbf{Description:} New users should be able to complete account setup and
understand core application features within five minutes, supported by an
introductory tutorial and tooltips.

\textbf{Type:} Manual, Usability Testing
					
\textbf{Initial State:} The application is installed and running. The state of
the application is not authenticated.
					
\textbf{Input/Condition:} A user performs various actions, including:
  \begin{itemize}
      \item Uploading a large receipt, causing a system processing delay
      \item Entering an invalid file format for receipt upload
      \item Attempting to categorize an expense while offline
  \end{itemize}
					
\textbf{Output/Result:} The user should have a new account created and
understand the core features of the application.
					
\textbf{How the Test Will Be Performed:} The user/tester will simulate a new
user experience, timing the setup and assessing the clarity of tutorials,
tooltips, error messages, and corrective guidance.

\item{test-USAB-3\\}

\textbf{Description:} Information displayed to users must be concise and
relevant, minimizing cognitive effort while ensuring that only essential details
are shown on the main dashboard, with advanced options accessible through menus.

\textbf{Type:} Manual, Usability Testing
					
\textbf{Initial State:} The application is displaying its main dashboard.
					
\textbf{Input/Condition:} The user/tester reviews the main dashboard and
navigates through the menus. A user triggers different error conditions, such as:
  \begin{itemize}
      \item Uploading an unsupported file format (e.g., `.txt`)
      \item Submitting a blank required field in an expense form
      \item Experiencing a timeout when fetching past transactions
      \item Entering an invalid number format (e.g., letters in a currency field)
  \end{itemize}
					
\textbf{Output/Result:} All information is displayed and menus open upon
command.
					
\textbf{How the Test Will Be Performed:} The user/tester will evaluate the main
dashboard and menus for clarity, relevance, and ease of access, ensuring the
design aligns with the usability requirements.

\item{test-USAB-4\\}

\textbf{Description:} Users should be able to recognize and recover from errors with clear guidance.

\textbf{Type:} Manual, Usability Testing
					
\textbf{Initial State:} The application is installed and running.
					
\textbf{Input/Condition:} A user attempts to perform an action that results in an error, including but not limited to:
\begin{itemize}
    \item Network disconnection during receipt upload
    \item Uploading an unsupported file format
    \item System timeout during data processing
    \item Uploading a corrupted or unreadable receipt image
\end{itemize}

\textbf{Output/Result:} The user should understand the error through clear messaging and be able to take corrective actions to resolve it.

\textbf{How the Test Will Be Performed:} The user/tester will intentionally trigger different error scenarios and assess:
\begin{itemize}
    \item Whether the system correctly detects the error
    \item The clarity of the displayed error message
    \item The ease of taking corrective actions (e.g., retrying, re-uploading, or receiving alternative guidance)
\end{itemize}

\end{enumerate}

\subsubsection{Security Tests}

This subsection covers tests required to ensure the security and protection of user data within the system. \\
\textit{Nonfunctional Requirements: NFR18 - NFR19}

\begin{enumerate}

\item{test-SEC-1\\}

\textbf{Description:} Verify that passwords are securely stored and
authentication is required for all user actions.

\textbf{Type:} Inspection, Manual
					
\textbf{Initial State:} The system is fully deployed and operational.
					
\textbf{Input/Condition:} A tester attempts to use SQL injection to access
the application.
					
\textbf{Output/Result:} The tester should be unable to access the application.
					
\textbf{How the Test Will Be Performed:} The tester will attempt to use SQL
injection to access the application.

\end{enumerate}

\subsubsection{Maintainability Tests}

This subsection covers tests required to verify the maintainability and compatibility of the application. \\
\textit{Nonfunctional Requirements: NFR20 - NFR 22}

\begin{enumerate}

\item{test-MTB-1\\}

\textbf{Description:} New releases must maintain backward compatibility with
previous versions.

\textbf{Type:} Manual
					
\textbf{Initial State:} The application is ready for a new release.
					
\textbf{Input/Condition:} A new release is applied to the application, along
with dependency updates.
					
\textbf{Output/Result:} The system must output a confirmation message indicating
a successful update, and system logs should show no errors or disruptions.
					
\textbf{How the Test Will Be Performed:} The user/tester will apply the new
release and perform typical user actions to verify that the application
functions correctly with no errors or disruptions.

\item{test-MTB-2\\}

\textbf{Description:} Dependencies must be regularly updated.

\textbf{Type:} Automatic
					
\textbf{Initial State:} Dependencies are out of date.
					
\textbf{Input/Condition:} A new patch is applied to the application.
					
\textbf{Output/Result:} Dependencies are updated.
					
\textbf{How the Test Will Be Performed:} Regularly scheduled updates will be
applied to the application.

\item{test-MTB-3\\}

\textbf{Description:} The codebase must be covered by automated tests.

\textbf{Type:} Automatic
					
\textbf{Initial State:} The application is up to date.
					
\textbf{Input/Condition:} A new code change is made.
					
\textbf{Output/Result:} The pipeline runs automated tests and checks for
coverage. 
					
\textbf{How the Test Will Be Performed:} Tests and coverage will be monitored
using GitHub Actions. If coverage criteria is not met or if any tests fail, the
change will be blocked from merging.

\end{enumerate}

\subsubsection{Portability Tests}

This subsection covers tests required to assess the portability of the application across different platforms and environments. \\
\textit{Nonfunctional Requirements: NFR23 - NFR 26}

\begin{enumerate}

\item{test-PORT-1\\}

\textbf{Description:} The software shall be compatible with Android and iOS
mobile devices running the latest software.

\textbf{Type:} Automatic
					
\textbf{Initial State:} The application is deployed on Android and iOS devices.
					
\textbf{Input/Condition:} Users attempt to install and run the application.
					
\textbf{Output/Result:} The system outputs successful installation messages and
the application functions correctly on both platforms.
					
\textbf{How the Test Will Be Performed:} Automated tests will verify
installation and functionality on both devices.

\item{test-PORT-2\\}

\textbf{Description:} All data must be stored in platform-independent formats
(e.g., JSON, CSV), and any external APIs or third-party services must support
cross-platform usage.

\textbf{Type:} Automatic
					
\textbf{Initial State:} The application has data stored and is integrated with
external APIs.
					
\textbf{Input/Condition:} The user/tester requests data export and initiates API
calls.
					
\textbf{Output/Result:} The system outputs data in specified formats and returns
successful responses from APIs on both platforms.
					
\textbf{How the Test Will Be Performed:} Automated scripts will verify data
export formats and API integration on both Android and iOS.

\item{test-PORT-3\\}

\textbf{Description:} The system must operate in various network environments,
including Wi-Fi, cellular, and offline mode.

\textbf{Type:} Manual
					
\textbf{Initial State:} The application is installed and ready for testing.
					
\textbf{Input/Condition:} The user/tester simulates different network
environments.
					
\textbf{Output/Result:} The system outputs successful operation messages for
each network condition.
					
\textbf{How the Test Will Be Performed:} The user/tester will manually switch
between different network environments (Wi-Fi, cellular, offline) and observe
the application's behavior, checking for consistent functionality and
performance across each condition.

\end{enumerate}

\subsubsection{Reusability Tests}

This subsection covers tests required to evaluate the reusability of components and functionalities within the application. \\
\textit{Nonfunctional Requirements: NFR27 - NFR 30}

\begin{enumerate}

\item{test-REUS-1\\}

\textbf{Description:} The application must be developed using reusable components (e.g., UI components, API services) and adhere to the principle of separation of concerns, ensuring that business logic, data access, and presentation layers are kept separate.

\textbf{Type:} Manual
					
\textbf{Initial State:} The application is developed and ready for testing.
					
\textbf{Input/Condition:} The user/tester reviews the codebase and architecture.
					
\textbf{Output/Result:} The system must show evidence of reusable components and separate layers, with no code duplication.
					
\textbf{How the Test Will Be Performed:} The user/tester will conduct a manual code review to assess the architecture for reusable components, ensuring adherence to the principle of separation of concerns. They will document findings regarding code duplication and the organization of business logic, data access, and presentation layers.

\item{test-REUS-2\\}

\textbf{Description:} Common functionalities (e.g., receipt parsing, authentication) must be abstracted into reusable libraries, and design elements (e.g., icons, typography) must be created as reusable assets.

\textbf{Type:} Automatic
					
\textbf{Initial State:} The application is fully developed.
					
\textbf{Input/Condition:} The user/tester inspects libraries and design assets.
					
\textbf{Output/Result:} The system must output a report confirming that functionalities are encapsulated in reusable libraries and design assets are consistently applied across the application.
					
\textbf{How the Test Will Be Performed:} Automated tools will verify the presence of reusable libraries and assets.

\end{enumerate}

\subsubsection{Understandability Tests}

This subsection covers tests required to assess the understandability and clarity of the application and its documentation. \\
\textit{Nonfunctional Requirements: NFR31 - NFR 39}

\begin{enumerate}

\item{test-UND-1\\}

\textbf{Description:} To validate that the codebase is well-documented,
organized, and follows consistent naming conventions and coding standards.

\textbf{Type:} Static, Code Review/Walkthrough
					
\textbf{Initial State:} The codebase is up to date and ready for review.
					
\textbf{Input/Condition:} The inspector reviews the code and associated
documentation.
					
\textbf{Output/Result:} A review report containing a summary of the codebase's
documentation, organization, and adherence to coding standards.
					
\textbf{How the Test Will Be Performed:} A team of developers will conduct a
walkthrough of the codebase, using static analysis tools to check for
documentation completeness and adherence to naming conventions. A designated
reviewer will conduct a walkthrough of the API documentation and commit history,
checking for completeness and clarity. The results will be documented in a
compliance report, which will be reviewed by the development team.

\item{test-UND-2\\}

\textbf{Description:} To validate that the user interface (UI) is simple to
navigate and understand.

\textbf{Type:} Usability Test
					
\textbf{Initial State:} The application is up to date.
					
\textbf{Input/Condition:} The user/tester interacts with the UI.
					
\textbf{Output/Result:} A usability report containing feedback on the UI's
clarity and organization.
					
\textbf{How the Test Will Be Performed:} The user/tester will manually navigate
the UI and fill in a usability survey, providing feedback on the clarity and
organization of the interface.

\item{test-UND-3\\}

\textbf{Description:} To validate that error messages are clear to the user and
logs are informative to developers.

\textbf{Type:} Manual
					
\textbf{Initial State:} The application is up to date.
					
\textbf{Input/Condition:} The user/tester intentionally triggers an error.
					
\textbf{Output/Result:} The user will provide feedback on the clarity of the
error message, and the developers will assess the informativeness of the logs.
					
\textbf{How the Test Will Be Performed:} The user/tester will intentionally
trigger an error and provide feedback on the clarity of the error message. The
developers will review the logs to ensure they contain sufficient information to
diagnose the issue.

\end{enumerate}

\subsubsection{Regulatory Tests}

This subsection covers tests required to ensure compliance with relevant
regulations and standards. \\
\textit{Nonfunctional Requirements: NFR40 - NFR 41}

\begin{enumerate}

\item{test-REG-1\\}

\textbf{Description:} The system must comply with Canada's Privacy Act and
Financial Administration Act to ensure the privacy and security of user data and
the secure handling of financial information.

\textbf{Type:} Manual, Inspection
					
\textbf{Initial State:} The application is up to date.
					
\textbf{Input/Condition:} An inspector reviews the system's data handling
policies and financial procedures.
					
\textbf{Output/Result:} The system must demonstrate adherence to both regulatory
acts through documented policies and secure practices.
					
\textbf{How the Test Will Be Performed:} The inspector will examine relevant
documentation, assess data handling procedures, and conduct interviews with
compliance and development teams to verify compliance with both the Privacy Act
and the Financial Administration Act.

\end{enumerate}


\subsection{Traceability Between Test Cases and Requirements}

A traceability matrix between test cases and requirements can be found
\href{https://github.com/PlutosCapstone/Plutos/blob/main/docs/VnVPlan/traceability_tests_and_requirements.xlsx}{here}.

\newpage

\section{Unit Test Description}

This section will be filled after completion of the MIS document.
% \wss{This section should not be filled in until after the MIS (detailed design
%   document) has been completed.}

% \wss{Reference your MIS (detailed design document) and explain your overall
% philosophy for test case selection.}  

% \wss{To save space and time, it may be an option to provide less detail in this section.  
% For the unit tests you can potentially layout your testing strategy here.  That is, you 
% can explain how tests will be selected for each module.  For instance, your test building 
% approach could be test cases for each access program, including one test for normal behaviour 
% and as many tests as needed for edge cases.  Rather than create the details of the input 
% and output here, you could point to the unit testing code.  For this to work, you code 
% needs to be well-documented, with meaningful names for all of the tests.}

\subsection{Unit Testing Scope}

This section will be filled after completion of the MIS document.

% \wss{What modules are outside of the scope.  If there are modules that are
%   developed by someone else, then you would say here if you aren't planning on
%   verifying them.  There may also be modules that are part of your software, but
%   have a lower priority for verification than others.  If this is the case,
%   explain your rationale for the ranking of module importance.}

\subsection{Tests for Functional Requirements}

This section will be filled after completion of the MIS document.

% \wss{Most of the verification will be through automated unit testing.  If
%   appropriate specific modules can be verified by a non-testing based
%   technique.  That can also be documented in this section.}

% \subsubsection{Module 1}

% \wss{Include a blurb here to explain why the subsections below cover the module.
%   References to the MIS would be good.  You will want tests from a black box
%   perspective and from a white box perspective.  Explain to the reader how the
%   tests were selected.}

% \begin{enumerate}

% \item{test-id1\\}

% Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
%   be automatic}
					
% \textbf{Initial State:} 
					
% \textbf{Input:} 
					
% \textbf{Output:} \wss{The expected result for the given inputs}

% \textbf{Test Case Derivation:} \wss{Justify the expected value given in the Output field}

% \textbf{How test will be performed:} 
					
% \item{test-id2\\}

% Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
%   be automatic}
					
% \textbf{Initial State:} 
					
% \textbf{Input:} 
					
% \textbf{Output:} \wss{The expected result for the given inputs}

% \textbf{Test Case Derivation:} \wss{Justify the expected value given in the Output field}

% \textbf{How test will be performed:} 

% \item{...\\}
    
% \end{enumerate}

% \subsubsection{Module 2}

% ...

\subsection{Tests for Nonfunctional Requirements}

This section will be filled after completion of the MIS document.

% \wss{If there is a module that needs to be independently assessed for
%   performance, those test cases can go here.  In some projects, planning for
%   nonfunctional tests of units will not be that relevant.}

% \wss{These tests may involve collecting performance data from previously
%   mentioned functional tests.}

% \subsubsection{Module ?}
		
% \begin{enumerate}

% \item{test-id1\\}

% Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
%   be automatic}
					
% \textbf{Initial State:} 
					
% Input/Condition: 
					
% Output/Result: 
					
% \textbf{How test will be performed:} 
					
% \item{test-id2\\}

% Type: Functional, Dynamic, Manual, Static etc.
					
% \textbf{Initial State:} 
					
% \textbf{Input:} 
					
% \textbf{Output:} 
					
% \textbf{How test will be performed:} 

% \end{enumerate}

% \subsubsection{Module ?}

% ...

\subsection{Traceability Between Test Cases and Modules}

This section will be filled after completion of the MIS document.

% \wss{Provide evidence that all of the modules have been considered.}

\newpage

\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\noindent
\\No references were used for this document.

\newpage

% \subsection{Usability Survey Questions?}

% \wss{This is a section that would be appropriate for some projects.}


\newpage

\section*{Appendix A --- Usability Survey Questions}
\label{appx.a}

\begin{enumerate}
    \item \textbf{Overall Experience}
    \begin{itemize}
        \item On a scale of 1 to 5, how easy was it to scan and upload receipts? (1 = Very Difficult, 5 = Very Easy)
        \item On a scale of 1 to 5, how intuitive was the app’s interface? (1 = Not Intuitive, 5 = Very Intuitive)
        \item On a scale of 1 to 5, how satisfied are you with the accuracy of the receipt scanning and categorization? (1 = Not Satisfied, 5 = Very Satisfied)
    \end{itemize}

    \item \textbf{Receipt Scanning and AI Parsing}
    \begin{itemize}
        \item Did you experience any difficulties capturing clear images of receipts? (Yes/No)
        \item Did the app correctly categorize your spending based on the receipt items? (Yes/No)
        \item If the app made mistakes in categorization, were you able to correct them easily? (1 = Very Difficult, 5 = Very Easy)
    \end{itemize}
    
    \item \textbf{Budgeting and Spending Insights}
    \begin{itemize}
        \item Did the budgeting feature help you understand your spending patterns? (1 = Not at All, 5 = Very Much)
        \item How clear was it to see the difference between your actual spending and budgeted amount? (1 = Not Clear, 5 = Very Clear)
        \item How useful were the insights provided about expected vs. actual spending? (1 = Not Useful, 5 = Very Useful)
    \end{itemize}
    
    \item \textbf{User Interface and Design}
    \begin{itemize}
        \item On a scale of 1 to 5, how visually appealing did you find the app’s design? (1 = Not Appealing, 5 = Very Appealing)
        \item Was the layout of information easy to understand? (1 = Very Confusing, 5 = Very Clear)
        \item Were you able to navigate between features without confusion? (Yes/No)
    \end{itemize}

    \item \textbf{Error Handling and Support}
    \begin{itemize}
        \item Did you encounter any errors or issues during your experience? (Yes/No)
        \item If yes, how helpful were the error messages in resolving the issue? (1 = Not Helpful, 5 = Very Helpful)
        \item Do you feel that any features or support options are missing? (Yes/No)
    \end{itemize}
    
    \item \textbf{Overall Satisfaction and Feedback}
    \begin{itemize}
        \item How likely are you to use this app regularly? (1 = Not Likely, 5 = Very Likely)
        \item Which feature did you find most useful? (Select all that apply: Receipt Scanning, Spending Categorization, Budget Tracking, Savings Calculation, Spending Insights)
        \item Would you recommend this app to others? (Yes/No)
    \end{itemize}
\end{enumerate}

\newpage{}
\section*{Appendix B --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.

\begin{enumerate}
  \item What went well while writing this deliverable? 

During this deliverable, the group divided the work up well through delegating
certain sections to each member to complete. Each group member was able to
seamlessly complete their section without many issues and conflicts. This was
prevelant through the PR review process where there were minimal comments for
each PR.

  \item What pain points did you experience during this deliverable, and how
    did you resolve them?

Some pain points that the group discussed was what we want to include in Rev0 of
the VnV plan. There were some scope issues that we discussed, specifically
around which functional requirements we want to include in the initial draft and
include tests for. Additionlly, the team discussed the granularity of the tests
that we want to include in the Rev0 VnV document. The group did not initially
agree on whether to include unit tests into this document. The team brought it
up, discussed it and in the end came to a conclusion of not including unit tests
within this document because the components/units to test have not yet been
designed in detail.

  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete the verification and validation of your project?
  Examples of possible knowledge and skills include dynamic testing knowledge,
  static testing knowledge, specific tool usage, Valgrind etc.  You should look to
  identify at least one item for each team member.

The team will collectively need to look into how to test machine learning models
as this topic is new for all group members. We will also need to look into
setting up GitHub Actions for continuous integration, so that we can implement
automated testing and code coverage. A few of us have utilized GitHub Actions at
previous co-ops and can utilize that knowledge to help set up GitHub Actions for
the Plutos project. Specifically, this will be the breakdown per team member:\\
\begin{itemize}
	\item Payton: Familiarize with continuous integration and how to set up GitHub
	Actions for automated testing and code coverage
	\item Eric: Deepen knowledge on backend testing frameworks and how to reach
	a high code coverage
	\item Fondson: Deepen knowledge on frontend testing frameworks, and ways to
	simulate user interactions for end-to-end testing
	\item Jason: Learn more about how to best conduct usability testing to
	evaluate user experiences, identify pain points, and improve the overall
	design and functionality of the project
	\item Angela: Familiarize with static testing tools and techniques to
	identify code quality issues and ensure the codebase follows best practices
\end{itemize}

  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?

All group members are currently taking or have taken Introduction to Machine
Learning (4ML3), and Jason is currently taking Applications of Machine Learning
(4AL3). Through these courses, we can learn about how to test machine learning
models, which would be the most difficult part of the project to test. \\
For the other knowledge areas, our team has all decided that we will use a
combination of YouTube and Coursera/LinkedIn Learning. We have decided that
these resources are the most straightforward to learn from and we all learn best
from watching videos and putting them to practice. For GitHub Actions, we will
also consult GitHub documentation as it would be the most reliable source of
information for setting it up and understanding how it works.


\end{enumerate}


\end{document}